---
title: "create map"
output: html_document
editor_options: 
  chunk_output_type: console
---


This markdown uses to leaflet to create interactive maps of the data. Leaflet can produce freestanding html files containing all data necessary to show your data superimposed over openstreetmap maps.

This markdown is supposed to be run after running "London_empty_homes.Rmd" which is why not data is loaded.

#Load packages

```{r}

packages <- c("dplyr", "ggplot2", "rjson", "jsonlite", "leaflet", "RCurl")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

lapply(packages, library, character.only = TRUE)
```

```{r}
MSOAshape2 <- MSOAshape %>%
    filter(name == "offshore") %>%
    mutate(value  = value) %>%
    st_transform(., crs =4326) %>%
    left_join(DATAdf %>% select(msoa11cd = MSOA11CD, homes = MSOAHomes) %>% distinct()) %>%
    mutate(value = 100*value/homes)

MSOAshape2 <- LSOAshape %>%
    filter(name == "low_use") %>%
    mutate(value  = value) %>%
    st_transform(., crs =4326) %>%
    left_join(DATAdf %>% select(lsoa11cd = LSOA11CD, homes = Homes) %>% distinct()) %>%
    mutate(value = 100*value/homes)


type = "Low Use"

{
  m <- MSOAshape2
  bbox_df <- st_bbox(m)
  m <- m %>%
    leaflet(.) %>%
    addTiles() %>%
    setView(0, 51.48, zoom = 10) %>%
  fitBounds(lng1 = bbox_df[[1]], lat1 =  bbox_df[[2]], lng2 =  bbox_df[[3]], lat2 =  bbox_df[[4]])
  
}

 bins = c(0, 5, 10, 20, 100)
pal <- colorBin("YlOrRd", domain = states$density, bins = bins)


  labels <- sprintf(
    paste0("<strong>%s</strong><br/>", type ,"  %g &#37"),
    MSOAshape2$lsoa11nm, round(MSOAshape2$value,3)
  ) %>% lapply(htmltools::HTML)


  out <-m %>% addPolygons(
    fillColor = ~pal(value),
    weight = 2,
    opacity = 0.5,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlight = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>%
    addLegend(pal = pal, values = ~density, opacity = 0.7, title = NULL,
              position = "bottomright")

```

# Whole UK

This is to make a map of the whole uk showing where I have data

```{r}

scotland_data <-read_csv(file.path("/home/jonno/empty_homes_data", "household-estimates.csv"), name_repair = 'universal') %>%
  rename(Homes = Total.Dwellings,
         LAD11CD = geography,
         LAD11NM = Reference.Area) %>%
  mutate(LowUse = Which.Are.Long.term.empty + Which.Are.Second.Homes + Which.Are.Vacant,
        LAD11CD = str_remove(LAD11CD, ".*/") )

LADshapedata <-
  "~/Dropbox/SSE/Empty Homes/ShapeFiles/Local_Authority_Districts_December_2014_Ultra_Generalised_Clipped_Boundaries_in_Great_Britain"

LADshape <- st_read(LADshapedata) %>%
  left_join(bind_rows(LAD_summary %>% select(LAD11CD, LAD11NM, Homes, LowUse), scotland_data), by = c('lad14cd' = 'LAD11CD')) %>%
  mutate(data_present = ifelse(!is.na(LowUse)|(grepl("S",lad14cd)), TRUE, FALSE))  %>%
    st_transform(., crs =4326)

{
  m <- LADshape
  bbox_df <- st_bbox(m)
  m <- m %>%
    leaflet(.) %>%
    addTiles() %>%
    setView(0, 51.48, zoom = 10) %>%
    fitBounds(
      lng1 = bbox_df[[1]],
      lat1 =  bbox_df[[2]],
      lng2 =  bbox_df[[3]],
      lat2 =  bbox_df[[4]]
    )
  
  }


pal <- colorFactor("YlOrRd", domain = c(TRUE, FALSE))

type = "Low Use"

labels <- sprintf(
  paste0("<strong>%s</strong><br/>", type , "  %g "),
  LADshape$lad14nm,
  LADshape$LowUse
) %>% lapply(htmltools::HTML)

out <- m %>% addPolygons(
  fillColor = ~ pal(data_present),
  weight = 2,
  opacity = 0.5,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7,
  highlight = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE
  ),
  label = labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto"
  )
)%>%
  addLegend(
    pal = pal,
    values = ~ c(TRUE, FALSE),
    opacity = 0.7,
    title = NULL,
    position = "bottomright"
  )
  
```

